The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-15 talk/vmil2012/paper.tex
cite some of our papers and don't mention .net/java too promoninently as targets

The RPython language and the PyPy project were started in 2002 with the goal of
creating a Python interpreter written in a high level language, allowing easy
language experimentation and extension. PyPy is now a fully compatible
alternative implementation of the Python language, that is on average about 5 times faster than the reference implementation. The
implementation takes advantage of the language features provided by RPython
such as the provided tracing just-in-time compiler described below.

RPython, the language and the toolset originally developed to implement the
Python interpreter have developed into a general environment for experimenting
and developing fast and maintainable dynamic language implementations. There
are, besides the Python interpreter, implementations of Prolog, Javascript, R,
Smalltalk among other that are written in RPython at different levels of
completeness.

RPython is constructed from two components:
\begin{itemize}
 \item the language itself
 \item the translation toolchain used to transform RPython programs to executable units
\end{itemize}
The RPython language
is a statically typed object oriented high level language. The language provides
several features such as automatic memory management
and just-in-time compilation. When writing an interpreter using RPython the
programmer only has to write the interpreter for the language she is
implementing.  The second RPython component, the translation toolchain, is used
to transform the program to a low level representations suited to be compiled
and run on one of the different supported target platforms/architectures such
as C, .NET and Java. During the transformation process
different low level aspects suited for the target environment are automatically
added to the program such as (if needed) a garbage collector
and based on hints provided by the author a just-in-time compiler.

>>>>

The RPython language and the PyPy project were started in 2002 with the goal of
creating a Python interpreter written in a high level language, allowing easy
language experimentation and extension. PyPy is now a fully compatible
alternative interpreter for the Python language.
Using RPython's tracing JIT compiler it is on average about 5 times faster than
CPython, the reference implementation.
PyPy is an interpreter written in RPython and takes advantage of the language
features provided by RPython
such as the provided tracing just-in-time compiler described below.

RPython, the language and the toolset originally developed to implement the
Python interpreter have developed into a general environment for experimenting
and developing fast and maintainable dynamic language implementations. There
are, besides the Python interpreter, experimental implementations of
Prolog~\cite{bolz_towards_2010}, Javascript, R,
Smalltalk~\cite{bolz_towards_2010} among other that are written in RPython at
different levels of completeness.

RPython can mean one of two things:
\begin{itemize}
 \item the language itself
 \item the translation toolchain used to transform RPython programs to executable units
\end{itemize}
The RPython language
is a statically typed object-oriented high level language. The language provides
several features such as automatic memory management
and just-in-time compilation. When writing an interpreter using RPython the
programmer only has to write the interpreter for the language she is
implementing.  The second RPython component, the translation toolchain, is used
to transform the interpreter into a C program.\footnote{
    RPython can also be used to translate programs to CLR and Java
    bytecode~\cite{ancona_rpython:_2007}, but this feature is somewhat
    experimental.
}
During the transformation process
different low level aspects suited for the target environment are automatically
added to the program such as a garbage collector and a tracing JIT compiler.
The process of inserting a tracing JIT is not fully automatic but is guided by
hints from the interpreter author.
